---
title: "Homework 1"
author: "Satya Batna"
date: "2025-09-20"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)   
library(moderndive)  
```

# Load the dataset
```{r}
data("early_january_weather")
```
This data set has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. This data is the hourly temperature from EWR in 2013. The variables that are listed are origin, year, day, time, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust,precip, pressure, visib, and time_hour.With mean `r  mean(early_january_weather$temp, na.rm = TRUE)` degrees.
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point(alpha = 0.8) +
  labs(
    x = "Time (hours)",
    y = "Temperature (°F)",
    color = "Humidity",
    title = "EWR temperature across early January 2013"
  ) +
  theme_minimal()
```
This scatterplot shows us the increasing in temperature over time and for lower humidity we have higher temperatures. 

```{r}
ggsave ("scatter_plot.pdf", height = 4, width = 6)

```

#Problem 2

set.seed(123)

```{r}
set.seed(123)

df <- tibble(
  norm_sample = rnorm(10),                         
  is_positive = rnorm(10) > 0,                      
  char_vec    = sample(letters, 10),                
  fact_vec    = factor(sample(c("low", "med", "high"), 10, replace = TRUE))
)

df
mean(pull(df,norm_sample))
mean(pull(df,is_positive))
mean(pull(df,char_vec))
mean(pull(df,fact_vec))

```
The character and factor vectors have errors show up for them but the random sample and logical vector do not give errors, but the logical vector seems to be false and I beleive the numbers are being binarized even though it is not binary.

```{r, results ='hide', warning=FALSE}
as.numeric(pull(df, is_positive)) 
as.numeric(pull(df, char_vec))    
as.numeric(pull(df, fact_vec))     

```
The logical vector is given directly as 1/0 and are automatically made to be true or false values with 1 and 0s even though they might not make sense. The character vector is given as NA's and the factor variables are given as their operationalzed numbers. You can interpret the character and factor variables. 


END OF HOMEWORK!!! This was a struggle frfr. 