---
title: "Homework 1"
author: "Satya Batna"
date: "2025-09-20"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)   
library(moderndive)  
```

# Load the dataset
```{r}
data("early_january_weather")
```
This data set has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. This data is the hourly temperature from EWR in 2013. The variables that are listed are origin, year, day, time, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust,precip, pressure, visib, and time_hour.With mean `r  mean(early_january_weather$temp, na.rm = TRUE)` degrees.
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point(alpha = 0.8) +
  labs(
    x = "Time (hours)",
    y = "Temperature (°F)",
    color = "Humidity",
    title = "EWR temperature across early January 2013"
  ) +
  theme_minimal()
```
This scatterplot shows us the increasing in temperature over time and for lower humidity we have higher temperatures. 

```{r}
ggsave ("scatter_plot.pdf", height = 4, width = 6)

```

#Problem 2

set.seed(123)

```{r}
set.seed(123)

df <- tibble(
  norm_sample = rnorm(10),                         
  is_positive = rnorm(10) > 0,                      
  char_vec    = sample(letters, 10),                
  fact_vec    = factor(sample(c("low", "med", "high"), 10, replace = TRUE))
)

df
mean(pull(df,norm_sample))
mean(pull(df,is_positive))
mean(pull(df,char_vec))
mean(pull(df,fact_vec))

```


